fdcoexist

### 2018-08-21 paper_simulations.Rmd
Synthetic plot improved: facet for type of envfilt and legend changes

no_compet_no_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width)
    })

```{r no_compet_no_cor_df_ind_landscape var_strength}
plot_no_compet_no_cor_df_ind_landscape = fig_ind_landscape(no_compet_no_cor_df,
                                                           no_compet_no_cor_label,
                                                           n_bins = 22,
                                                           given_trans = "identity")

@@

```{r simul_no_compet_low_cor var_strength}
no_compet_low_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = low_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width)
    })

```{r no_compet_low_cor_df_ind_landscape var_strength}
plot_no_compet_low_cor_df_ind_landscape = fig_ind_landscape(no_compet_low_cor_df,
                                                            no_compet_low_cor_label,
                                                            n_bins = 17,
                                                            given_trans = "identity")

@@

```{r simul_no_compet_high_cor var_strength}
no_compet_high_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = high_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width)
    })

```{r no_compet_high_cor_df_ind_landscape var_strength}
plot_no_compet_high_cor_df_ind_landscape = fig_ind_landscape(no_compet_high_cor_df,
                                                             no_compet_high_cor_label,
                                                             n_bins = 17)

@@

```{r simul_compet_no_corr var_strength}
compet_no_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width)
    })

```{r compet_no_cor_df_ind_landscape var_strength}
plot_compet_no_cor_df_ind_landscape = fig_ind_landscape(compet_no_cor_df,
                                                        compet_no_cor_label,
                                                        n_bins = 22)

@@

```{r simul_compet_low_corr var_strength}
compet_low_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width)
    })

```{r compet_low_cor_df_ind_landscape var_strength}
plot_compet_low_cor_df_ind_landscape = fig_ind_landscape(compet_low_cor_df,
                                                         compet_low_cor_label,
                                                         n_bins = 17)

@@

```{r simul_compet_high_corr var_strength}
compet_high_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width)
    })

```{r compet_high_cor_df_ind_landscape var_strength}
plot_compet_high_cor_df_ind_landscape = fig_ind_landscape(compet_high_cor_df,
                                                          compet_high_cor_label,
                                                          n_bins = 17)
plot_compet_high_cor_df_ind_landscape
```

>>>>

no_compet_no_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
no_compet_no_cor_var_df = tidy_simulation_list(no_compet_no_cor_var,
                                               set_of_traits = uncor_traits,
                                               trait_scenarios = trait_scenarios)

no_compet_no_cor_var_label = paste0("No competition; ",
                                    d * 100, "% dispersal;",
                                    " 3 uncorrelated traits")
```

```{r no_compet_no_cor_df_ind_landscape var_strength}
plot_no_compet_no_cor_df_ind_landscape = fig_ind_landscape(no_compet_no_cor_var_df,
                                                           no_compet_no_cor_var_label,
                                                           n_bins = 22,
                                                           given_trans = "identity")

@@

```{r simul_no_compet_low_cor var_strength}
no_compet_low_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = low_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
no_compet_low_cor_var_df = tidy_simulation_list(no_compet_low_cor_var,
                                                low_cor_traits,
                                                trait_scenarios)

no_compet_low_cor_var_label = paste0("No competition; ",
                                     d * 100, "% dispersal;",
                                     " 3 low correlated (r = 0.3) traits")
```

```{r no_compet_low_cor_df_ind_landscape var_strength}
plot_no_compet_low_cor_df_ind_landscape = fig_ind_landscape(no_compet_low_cor_var_df,
                                                            no_compet_low_cor_var_label,
                                                            n_bins = 17,
                                                            given_trans = "identity")

@@

```{r simul_no_compet_high_cor var_strength}
no_compet_high_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = high_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
no_compet_high_cor_var_df = tidy_simulation_list(no_compet_high_cor_var,
                                                 high_cor_traits,
                                                 trait_scenarios)

no_compet_high_cor_var_label = paste0("No competition; ",
                                      d * 100, "% dispersal;",
                                      " 3 high correlated (r = 0.7) traits")
```

```{r no_compet_high_cor_df_ind_landscape var_strength}
plot_no_compet_high_cor_df_ind_landscape = fig_ind_landscape(no_compet_high_cor_var_df,
                                                             no_compet_high_cor_var_label,
                                                             n_bins = 17)

@@

```{r simul_compet_no_corr var_strength}
compet_no_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
compet_no_cor_var_df = tidy_simulation_list(compet_no_cor_var,
                                            set_of_traits = uncor_traits,
                                            trait_scenarios = trait_scenarios)

compet_no_cor_var_label = paste0("Competition (A = ", A, "); ",
                                 d * 100, "% dispersal;",
                                 " 3 uncorrelated traits")
```

```{r compet_no_cor_df_ind_landscape var_strength}
plot_compet_no_cor_df_ind_landscape = fig_ind_landscape(compet_no_cor_var_df,
                                                        compet_no_cor_var_label,
                                                        n_bins = 22)

@@

```{r simul_compet_low_corr var_strength}
compet_low_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
compet_low_cor_var_df = tidy_simulation_list(compet_low_cor_var,
                                             set_of_traits = low_cor_traits,
                                             trait_scenarios = trait_scenarios)

compet_low_cor_var_label = paste0("Competition (A = ", A, "); ",
                                  d * 100, "% dispersal;",
                                  " 3 correlated traits (r = 0.3)")
```

```{r compet_low_cor_df_ind_landscape var_strength}
plot_compet_low_cor_df_ind_landscape = fig_ind_landscape(compet_low_cor_var_df,
                                                         compet_low_cor_var_label,
                                                         n_bins = 17)

@@

```{r simul_compet_high_corr var_strength}
compet_high_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
compet_high_cor_var_df = tidy_simulation_list(compet_high_cor_var,
                                              set_of_traits = high_cor_traits,
                                              trait_scenarios = trait_scenarios)

compet_high_cor_var_label = paste0("Competition (A = ", A, "); ",
                                   d * 100, "% dispersal;",
                                   " 3 correlated traits (r = 0.7)")
```

```{r compet_high_cor_df_ind_landscape var_strength}
plot_compet_high_cor_df_ind_landscape = fig_ind_landscape(compet_high_cor_var_df,
                                                          compet_high_cor_var_label,
                                                          n_bins = 17)
plot_compet_high_cor_df_ind_landscape
```

# Synthetic plot

```{r synthetic_plot}

list_df <- list("no_compet_no_cor_df" = no_compet_no_cor_df,
                "no_compet_low_cor_df" = no_compet_low_cor_df,
                "no_compet_high_cor_df" = no_compet_high_cor_df,
                "compet_no_cor_df" = compet_no_cor_df,
                "compet_low_cor_df" = compet_low_cor_df,
                "compet_high_cor_df" = compet_high_cor_df)
list_df <- mapply(cbind, list_df, "var_df" = names(list_df),
                  SIMPLIFY = FALSE)
list_df <- lapply(list_df, function(x) data.frame(x, type = "constant"))

list_var_df <- list("no_compet_no_cor_var_df" = no_compet_no_cor_var_df,
                    "no_compet_low_cor_var_df" = no_compet_low_cor_var_df,
                    "no_compet_high_cor_var_df" = no_compet_high_cor_var_df,
                    "compet_no_cor_var_df" = compet_no_cor_var_df,
                    "compet_low_cor_var_df" = compet_low_cor_var_df,
                    "compet_high_cor_var_df" = compet_high_cor_var_df)
list_var_df <- mapply(cbind, list_var_df, "var_df" = names(list_var_df),
                      SIMPLIFY = FALSE)
list_var_df <- lapply(list_var_df, function(x) data.frame(x, type = "varying"))

all_list <- c(list_df, list_var_df)

all_df <- as.data.frame(bind_rows(all_list))

# List of weighted linear regressions
trait2_w_lm = all_df %>%
    group_by(var_df, scenario) %>%
    do(model = lm(trait2 ~ patch_optim, data = ., weights = N))

list_lm_df <- trait2_w_lm[[1]]
list_lm_scenario <- trait2_w_lm[[2]]

trait2_w_lm <- lapply(trait2_w_lm$model, summary)

synth_plot <- data.frame(df = list_lm_df,
                         scenario = list_lm_scenario,
                         r2 = unlist(lapply(trait2_w_lm,
                                            function(x) x$r.squared)))

synth_plot$df <- as.factor(synth_plot$df)
synth_plot$df <- factor(synth_plot$df,
                        levels(synth_plot$df)[c(6:1)])
synth_plot$compet <- ifelse(grepl("no_compet", synth_plot$df), "No", "Competition")
synth_plot$type <- ifelse(grepl("_var_", synth_plot$df), "Varying", "Constant")

print(ggplot(synth_plot, aes(as.factor(df), r2)) +
          geom_point(aes(shape = as.factor(scenario),
                         fill = as.factor(compet)),
                     color = "black", size = 4) +
          scale_fill_manual("Competition", values = c(No = "#a50026",
                                                      Competition = "#313695")) +
          scale_shape_manual("Scenario", values = c(RA100100 = 21, RA2575 = 22,
                                                    RA5050 = 23, RA7525 = 24)) +
          facet_wrap(~ type) +
          labs(subtitle = "R2 for the weighted linear regression between trait2 and environment",
               x = "Scenario",
               y = expression("R"^2)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          guides(color = FALSE,
                 fill = guide_legend(override.aes = list(shape = 21,
                                                         size = 4))))

```
